---
title: "BIONESS_Quality_Control_Template"
author: "Emily O'Grady"
date: "2024-12-11"
output: html_document
---
This is a template for running quality control checks on the BIONESS data. 

This workflow is meant to confirm the quality of BIONESS plankton data before
loading to BioChem. The checks confirm the formatting of the data as well as
some common sense checks on the content of the taxonomic data. These checks were
developed in close coordination with Rebecca Milne, plankton taxonomist and 
subject matter expert.


The first step is to confirm that the data is properly formatted for loading. 
We check the headers against standard values and ensure that each columns 
has the expected data type (numeric or character value). 

The next step involves more detailed checks on the data based on standard 
expectations. The tests are each detailed in the function documentation. 

This document will run through all of the QC tests in 'quality_control.R' for 
each data file selected by the user. The output will be recorded in a text file named
based on the mission with the date and time of the run. 

```{r setup, include=FALSE}
library(tidyverse)
library(readxl)
library(here)
source(here('R/quality_control.R'))
dir.create(here('QC_output'), showWarnings = FALSE)
```

```{r, include=FALSE}

# choose files to be QC'd
files <- choose.files(default = 'R:/Science/BIODataSvc/SRC/ZPlankton_DataRescue/OGrady_2024/FINAL', multi = TRUE)
datafiles <- files[grep(pattern = "*_BIONESS.xlsx", x = files)]
metafiles <- files[grep(pattern = "*_Elog.xlsx", x = files)]

```



```{r}
for (i in 1:length(datafiles)) {
  
  # read in data
  data <- read_xlsx(datafiles[i], sheet = 1)
  if (length(metafiles) > 0){
    metadata <- read_excel(metafiles[i], sheet = 1)
  } else {
    metadata <- NULL
  }
  
# open output document named with mission name from data file
mission <- str_split_i(str_split_i(datafiles[i], "\\\\", -1), "_", 1)
output_file <- paste0(mission, "_QC_", Sys.Date(), ".txt")
sink(file.path(here('QC_output'), output_file))

# write header
cat(paste0("Quality Control Report for ", mission, "\n"))
cat(paste0("Date: ", Sys.Date(), '   ', format(Sys.time(), '%H:%M:%S'), "\n\n"))
cat("---------------------------------------------\n\n")

if (is.null(metadata)) {
  cat("No metadata file found.\n\n")
} 
 

# run QC tests on each file
plankton_data_check(data)

if (!is.null(metadata)) {
  plankton_metadata_check(data, metadata)
}

plankton_completeness_check(data)

plankton_calanalysis_check(data)

plankton_lganimal_check(data)

plankton_numeric_check(data)

plankton_split_check(data)

plankton_weight_check(data)

cat("All checks complete.\n")

sink()

}
```


